SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Update ActaInformatica.tex

\subsection{Algebra Presentations}
In practice, the parameterisation of the pNet model by some specific
action algebra is realised by the definition of a many-sorted algebra
presentation. It will be used to check the
well-formedness of a pNet system, and to define the translation of the pNet
semantics into the SMT engine input language (\cite{BarFT-RR-17}).

>>>>

\subsection{Algebra Presentations}
In practice, the parameterisation of the pNet model by some specific
action algebra is realised by the definition of a many-sorted algebra
presentation. It will be used to check the
well-formedness of a pNet system, and to define the translation of the pNet
semantics into the SMT engine input language (see \cite{BarFT-RR-17}).
